### 2024-07-17 basic-statistics.qmd
20240714 - cite package
20240716 - conditional probability notation

The mode is the most common/frequent value.
The mode of the values of 0, 0, 10, 15, 20, 30, and 1000 is `{r} exampleValues_mode`.

@@

This can be expressed in conditional probability notation, $Pr(A | B)$, which is the probability (likelihood) of event A occurring given that event B occurred (or given condition B).

@@

$$
p\text{-value} = Pr(T \le t | H_0)
$$ {#eq-pvalueLeftTailed}

@@

$$
p\text{-value} = Pr(T \ge t | H_0)
$$ {#eq-pvalueRightTailed}

@@

$$
p\text{-value} = 2 \times \text{min}(Pr(T \le t | H_0), Pr(T \ge t | H_0))
$$ {#eq-pvalueTwoTailed}

@@

$$
p\text{-value} = 2 \times Pr(T \ge |t| | H_0)
$$ {#eq-pvalueTwoTailedSimple}

>>>>

The mode is the most common/frequent value.
The mode of the values of 0, 0, 10, 15, 20, 30, and 1000 is `{r} exampleValues_mode`.
The [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] contains the `Mode()` function for computing the mode of a set of data.

@@

This can be expressed in conditional probability notation, $P(A | B)$, which is the probability (likelihood) of event A occurring given that event B occurred (or given condition B).

@@

$$
p\text{-value} = P(T \le t | H_0)
$$ {#eq-pvalueLeftTailed}

@@

$$
p\text{-value} = P(T \ge t | H_0)
$$ {#eq-pvalueRightTailed}

@@

$$
p\text{-value} = 2 \times \text{min}(P(T \le t | H_0), P(T \ge t | H_0))
$$ {#eq-pvalueTwoTailed}

@@

$$
p\text{-value} = 2 \times P(T \ge |t| | H_0)
$$ {#eq-pvalueTwoTailedSimple}
